The Free-play Sandbox: a Novel Methodology for the Evaluation of Social Robotics

### 2017-10-06 paper.tex
WIP on social annotations

\title{The Freeplay Sandbox: a Novel Methodology for the Evaluation of Social Robotics}

@@

The Freeplay Sandbox provides the opportunity to observe children interacting in a natural way in an open but framed setup. As the system can run on a single computer platform it can easily be deployed in the 'wild', in places where the children naturally interact such as classroom. The quantity and thoughtfulness of information logged allows to keep a track of every interaction happening around the game.

@@

\paragraph{Child-Robot Interaction}
\label{ssec|CRI}
This Freeplay Sandbox provides the opportunity to explore child-robot
interactions in this open-real world environment as shown in Figure
\ref{fig|freeplay}.

@@

\begin{table}[!]
\caption{Data acquisition protocol}
    \label{tab|protocol}
\centering
\begin{tabular}{p{\linewidth}}
\toprule
\bf Greetings \emph{(about 5 min)} \\
\tabitem explain the purpose of the study: showing robots how children play  \\
\tabitem briefly present a Nao robot: the robot stands up, gives a short
message, and sits down. \\
\tabitem place children on cushions \\ 
\tabitem complete demographics on the tablet \\
\tabitem remind the children that they can withdraw at anytime \\ \midrule
\bf Tutorial \emph{(1-2 min)}  \\
explain how to interact with the game, ensure the children are confident
with the manipulation/drawing \\ \midrule
\bf Freeplay task (up to 40 min)\\
\tabitem initial prompt: \emph{"Just to remind you, you can use the animals or draw. Whatever you
like. If you run out of ideas, there's also an ideas box. For example, the first one is a
zoo. You could draw a zoo or tell a story. When you get bored or don't want to play
anymore, just let me know."} \\
\tabitem let children play \\
\tabitem once they wish to stop, stop recording \\ \midrule
\bf Debriefing      \emph{(about 2 min)} \\
\tabitem answer possible questions from the children \\
\tabitem give small reward (\eg stickers) as a thank you \\ \bottomrule
\end{tabular}
\end{table}

@@

Annotating social interaction beyond surface behaviours is generally difficult:
as research scientists, the behaviours we observe are typically the result of a
superposition of complex and non-observable cognitive and emotional states. As
such, these interesting socio-cognitive states can only be indirectly observed,
and their labelling is error prone [TODO: citation needed].

@@

\subsection{Video Coding}

\todo{Mention the annotator tool}

@@

We have been using the Freeplay Sandbox task for an initial, large scale, data
collection over a period of 3 months during Spring 2017.

This campaign aimed at (1) extensively evaluating the task itself (would
children engage and exhibit a large range of social dynamics and behaviours?),
(2) making sure the whole software architecture and data acquisition pipeline
were reliable (they were), and (3) establishing two experimental baselines for
the Freeplay Sandbox task: the `human' baseline on one hand (child-child
condition), an `asocial' baseline on the other hand (child - \emph{non-social}
robot condition). These two baselines are situated at the two ends of the
spectrum of social interaction. They aim at characterising the qualitative and
quantitative bounds of this social spectrum and can be used by the research
community to evaluate given interaction policies.

@@

In the child-child condition (as seen in Figure~\ref{annotator}), 45 freeplay interactions (\ie 90 children) were
recorded with a duration M=24.15 min (SD=11.25 min).

>>>>

\title{The Free-play Sandbox: a Novel Methodology for the Evaluation of Social Robotics}

@@

The Free-play Sandbox provides the opportunity to observe children interacting in a natural way in an open but framed setup. As the system can run on a single computer platform it can easily be deployed in the 'wild', in places where the children naturally interact such as classroom. The quantity and thoughtfulness of information logged allows to keep a track of every interaction happening around the game.

@@

\paragraph{Child-Robot Interaction}
\label{ssec|CRI}
This Free-play Sandbox provides the opportunity to explore child-robot
interactions in this open-real world environment as shown in Figure
\ref{fig|freeplay}.

@@

\begin{table}[!]
\caption{Data acquisition protocol}
    \label{tab|protocol}
\centering
\begin{tabular}{p{\linewidth}}
\toprule
\bf Greetings \emph{(about 5 min)} \\
\tabitem explain the purpose of the study: showing robots how children play  \\
\tabitem briefly present a Nao robot: the robot stands up, gives a short
message, and sits down. \\
\tabitem place children on cushions \\ 
\tabitem complete demographics on the tablet \\
\tabitem remind the children that they can withdraw at anytime \\ \midrule
\bf Tutorial \emph{(1-2 min)}  \\
explain how to interact with the game, ensure the children are confident
with the manipulation/drawing \\ \midrule
\bf Free-play task (up to 40 min)\\
\tabitem initial prompt: \emph{"Just to remind you, you can use the animals or draw. Whatever you
like. If you run out of ideas, there's also an ideas box. For example, the first one is a
zoo. You could draw a zoo or tell a story. When you get bored or don't want to play
anymore, just let me know."} \\
\tabitem let children play \\
\tabitem once they wish to stop, stop recording \\ \midrule
\bf Debriefing      \emph{(about 2 min)} \\
\tabitem answer possible questions from the children \\
\tabitem give small reward (\eg stickers) as a thank you \\ \bottomrule
\end{tabular}
\end{table}

@@

Annotating social interaction beyond surface behaviours is generally difficult:
The observable, surface behaviours typically result of a superposition of the
complex and non-observable underlying cognitive and emotional states. As
such, these deeper socio-cognitive states can only be indirectly observed,
and their labelling is typically error prone.

@@

In our scheme, we characterise \emph{Social engagement} by building upon
Parten's stages of play. These 5 stages of play are normally
used to characterise rather long sequences (at least several minutes) of social
interactions.

However, instead of characterising long social
sequences (several minutes) with these 5 stages, we look at the micro-structure of the
interaction:

\paragraph{Social attitude}

The constructs related to the social \emph{attitude} of the children derive from the
\emph{Social Communication Coding System} (SCCS) proposed by
Olswang~\etal\cite{olswang2006reliability}.  The SCCS consists in 6 mutually
exclusive constructs characterising social communication (\emph{hostile};
\emph{pro-social}; \emph{assertive}; \emph{passive}; \emph{adult seeking};
\emph{irrelevant}) and were specifically created to characterise children
communication in a classroom setting.

We transpose these constructs from the communication domain to the general
behavioural domain, keeping the \emph{pro-social}, \emph{hostile} (whose scope
we broaden in \emph{adversarial}), \emph{assertive} (\ie dominant), and
\emph{passive} constructs. In our scheme, the \emph{adult seeking} and
\emph{irrelevant} constructs belong to Task Engagement axis.

Finally, we have added the construct \emph{Frustrated} to describe children who
are reluctant or refuse to engage in a specific phase of interaction
because of a perceived lack of fairness or attention from their peer, or because
they fail at achieving a particular task (like a drawing).

\paragraph{Video coding}

The coding is performed post-hoc with the help of a dedicated annotation tool
(Fig.~\ref{annotator} which is part of the Free-play sandbox toolbox. This tool
can replay and randomly seek in the three video streams, synchronised with the
recorded state of the game (including the drawings as they are created). An
interactive timeline displaying the annotations is also displayed.

The annotation tool offers a remote interface for the annotator (made of large
buttons, and visually similar to Figure~\ref{fig|coding-scheme}) that is
typically displayed on a tablet and allow the simultaneous coding of the
behaviours of the two children.  Usual video coding practices (double-coding of
a portion of the dataset and calculation of an inter-judge agreement score)
would have to be followed.

@@

We have been using the free-play Sandbox task for an initial, large scale, data
collection over a period of 3 months during Spring 2017.

This campaign aimed at (1) extensively evaluating the task itself (would
children engage and exhibit a large range of social dynamics and behaviours?),
(2) making sure the whole software architecture and data acquisition pipeline
were reliable (they were), and (3) establishing two experimental baselines for
the Free-play Sandbox task: the `human' baseline on one hand (child-child
condition), an `asocial' baseline on the other hand (child - \emph{non-social}
robot condition). These two baselines are situated at the two ends of the
spectrum of social interaction. They aim at characterising the qualitative and
quantitative bounds of this social spectrum and can be used by the research
community to evaluate given interaction policies.

@@

In the child-child condition (as seen in Figure~\ref{annotator}), 45 free-play interactions (\ie 90 children) were
recorded with a duration M=24.15 min (SD=11.25 min).
